``How Prolific Are You?": A Scientometric Analysis of Researchers

### 2018-12-18 paper/paper.tex
Changed to journal template

\documentclass[12pt,a4paper,twocolumn]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{authblk}
\usepackage[font=small,labelfont=bf]{caption}

\title{``How Prolific Are You?": A Scientometric Analysis of Researchers}

\author[1]{Rahul Yedida}
\author[2]{Adel Aladwani}
\author[1]{Snehanshu Saha}
\affil[1]{Department of Computer Science \& Engineering, PES University}
\affil[2]{Department of Information Systems, Kuwait University}

\date{}
\begin{document}
	\maketitle

	\abstract{
		Scholars in academia regularly write papers showing the results of their work. To gauge how relevant their work is, several measures are used, including citation count and the h-index. This paper describes the methods used to identify ``prolific" authors, whose metrics are significantly higher than their peers, and provides a general discussion of the relationships between different metrics. We also discuss how this analysis is performed even with the high dimensionality of the dataset.
	}

@@

	\begin{tabular}{|c|c|}
		\hline 
		\textbf{Cluster} & \textbf{Number of points} \\ 
		\hline 
		-1 & 60 \\ 
		\hline 
		0 & 532 \\ 
		\hline 
		1 & 20 \\ 
		\hline 
		2 & 6 \\ 
		\hline 
	\end{tabular}
	\begingroup
	\captionof{table}{DBSCAN clustering results on $S_1$}
	\endgroup
	\hfill\break

@@

	\begin{tabular}{|c|c|}
		\hline 
		\textbf{Cluster} & \textbf{Number of points} \\ 
		\hline 
		-1 & 5 \\ 
		\hline 
		0 & 509 \\ 
		\hline 
		1 & 72 \\ 
		\hline 
		2 & 19 \\ 
		\hline 
		3 & 4 \\ 
		\hline 
		4 & 4 \\ 
		\hline 
		5 & 3 \\ 
		\hline 
		6 & 2 \\ 
		\hline 
	\end{tabular}
	\begingroup
	\captionof{table}{Mean-Shift clustering results for $S_1$}
	\endgroup
	\hfill\break

@@

	\begin{tabular}{|c|c|}
		\hline 
		\textbf{Cluster} & \textbf{Number of points} \\ 
		\hline 
		-1 & 60 \\ 
		\hline 
		0 & 541 \\ 
		\hline 
		1 & 3 \\ 
		\hline 
		2 & 14 \\ 
		\hline 
	\end{tabular} 
	\begingroup
	\captionof{table}{DBSCAN clustering results for $S_2$}
	\endgroup
	\hfill\break

@@

	\begin{tabular}{|c|c|}
		\hline 
		\textbf{Cluster} & \textbf{Number of points} \\ 
		\hline 
		-1 & 8 \\ 
		\hline 
		0 & 504 \\ 
		\hline 
		1 & 82 \\ 
		\hline 
		2 & 15 \\ 
		\hline 
		3 & 3 \\ 
		\hline 
		4 & 2 \\ 
		\hline 
		5 & 2 \\ 
		\hline 
		6 & 2 \\ 
		\hline 
	\end{tabular} 
	\begingroup
	\captionof{table}{Mean-Shift clustering results for $S_2$}
	\endgroup
	\hfill\break

@@

	\begin{tabular}{|c|c|c|c|}
		\hline 
		$C_1$ & $C_2$ & \textbf{95\%} & \textbf{90\%} \\ 
		\hline 
		-1 & 0 & 1.0 & 1.0 \\ 
		\hline 
		-1 & 1 & 0.857 & 0.857 \\ 
		\hline 
		-1 & 2 & 0.928 & 1.0 \\ 
		\hline 
		0 & 1 & 0.786 & 0.857 \\ 
		\hline 
		0 & 2 & 1.0 & 1.0 \\ 
		\hline 
		1 & 2 & 0.643 & 0.786 \\ 
		\hline 
	\end{tabular} 
	\begingroup
	\captionof{table}{Fraction of significant Welch's test p-values at 95\% and 90\% confidence levels}
	\endgroup
	\hfill\break

>>>>

\documentclass[smallextended]{svjour3} 
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{authblk}
\usepackage[font=small,labelfont=bf]{caption}

\begin{document}
\title{``How Prolific Are You?": A Scientometric Analysis of Researchers}

\author{Rahul Yedida \and Adel Aladwani \and Snehanshu Saha}

\institute{Rahul Yedida \at
              Department of Computer Science and Engineering \\ PES University, Electronic City Campus \\
              Tel.: +91 8066186610\\
              \email{y.rahul@outlook.com}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
           Adel Aladwani \at
              Department of Information Systems\\Kuwait University
           \and
           Snehanshu Saha \at
              Department of Computer Science\\
              PES University
}

\date{Received: date / Accepted: date}
	\maketitle

\begin{abstract}
Scholars in academia regularly write papers showing the results of their work. To gauge how relevant their work is, several measures are used, including citation count and the h-index. This paper describes the methods used to identify ``prolific" authors, whose metrics are significantly higher than their peers, and provides a general discussion of the relationships between different metrics. We also discuss how this analysis is performed even with the high dimensionality of the dataset.

\keywords{scientometrics \and DBSCAN \and PCA \and Mean Shift}
\end{abstract}

@@

	\begingroup
	\captionof{table}{DBSCAN clustering results on $S_1$}
	\endgroup
	\begin{tabular}{ll}
		\hline 
		\textbf{Cluster} & \textbf{Number of points} \\ 
		\hline 
		-1 & 60 \\ 
		\hline 
		0 & 532 \\ 
		\hline 
		1 & 20 \\ 
		\hline 
		2 & 6 \\ 
		\hline 
	\end{tabular}
	\hfill\break

@@

	\begingroup
	\captionof{table}{Mean-Shift clustering results for $S_1$}
	\endgroup
	\begin{tabular}{ll}
		\hline 
		\textbf{Cluster} & \textbf{Number of points} \\ 
		\hline 
		-1 & 5 \\ 
		\hline 
		0 & 509 \\ 
		\hline 
		1 & 72 \\ 
		\hline 
		2 & 19 \\ 
		\hline 
		3 & 4 \\ 
		\hline 
		4 & 4 \\ 
		\hline 
		5 & 3 \\ 
		\hline 
		6 & 2 \\ 
		\hline 
	\end{tabular}

	\hfill\break

@@

	\begingroup
	\captionof{table}{DBSCAN clustering results for $S_2$}
	\endgroup
	\begin{tabular}{ll}
		\hline 
		\textbf{Cluster} & \textbf{Number of points} \\ 
		\hline 
		-1 & 60 \\ 
		\hline 
		0 & 541 \\ 
		\hline 
		1 & 3 \\ 
		\hline 
		2 & 14 \\ 
		\hline 
	\end{tabular}

	\hfill\break

@@

	\begin{tabular}{ll}
		\hline 
		\textbf{Cluster} & \textbf{Number of points} \\ 
		\hline 
		-1 & 8 \\ 
		\hline 
		0 & 504 \\ 
		\hline 
		1 & 82 \\ 
		\hline 
		2 & 15 \\ 
		\hline 
		3 & 3 \\ 
		\hline 
		4 & 2 \\ 
		\hline 
		5 & 2 \\ 
		\hline 
		6 & 2 \\ 
		\hline 
	\end{tabular} 
	\begingroup
	\captionof{table}{Mean-Shift clustering results for $S_2$}
	\endgroup
	\hfill\break

@@

	\begingroup
	\captionof{table}{Fraction of significant Welch's test p-values at 95\% and 90\% confidence levels}
	\endgroup
	\begin{tabular}{llll}
		\hline 
		$C_1$ & $C_2$ & \textbf{95\%} & \textbf{90\%} \\ 
		\hline 
		-1 & 0 & 1.0 & 1.0 \\ 
		\hline 
		-1 & 1 & 0.857 & 0.857 \\ 
		\hline 
		-1 & 2 & 0.928 & 1.0 \\ 
		\hline 
		0 & 1 & 0.786 & 0.857 \\ 
		\hline 
		0 & 2 & 1.0 & 1.0 \\ 
		\hline 
		1 & 2 & 0.643 & 0.786 \\ 
		\hline 
	\end{tabular}

	\hfill\break
